{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-18 documents/charge.tex
data

As might be expected, the electrostatic properties of the virus differ from that of host cells, both \cite{Icosahedral2019} on the sub-protein level:

\begin{quote}
	Different from insect, plant, and human, viruses had more positively charged than negatively charged segments. In Fig. 1B we show the log (base 10) net-charge frequency value for a selected group of proteins (e.g., Viral proteins) subtracted of the log expected frequency value calculated from the total proteome distribution (i.e., log10-fold-change). Viral proteins were the only class enriched in extremely high positively charged segments (charge ≥ + 17) when compared to the overall proteome (1B-inset with p-values).
\end{quote}

@@

todo: is it possible for the charged core to compensate for the potential energy of the charged shell?

>>>>

As might be expected, the electrostatic properties of the virus differ from that of host cells, both on the sub-protein level\footnotemark

\footnotetext{
\cite{Icosahedral2019}\begin{quote}
	Different from insect, plant, and human, viruses had more positively charged than negatively charged segments. Viral proteins were the only class enriched in extremely high positively charged segments (charge ≥ + 17) when compared to the overall proteome (1B-inset with p-values).
\end{quote}
}

@@

\begin{autem}
TODO: is it possible for the charged core to compensate for the potential energy of the charged shell?
\end{autem}

Using electroporation data, is osmotic transfer a common

If the intracellular concentration of 500 mM of ions  from https://www.cell.com/action/showPdf?pii=S0006-3495%2899%2976974-2 is extrapolated to viruses,

$500 millimolar * (4/3 pi * ( 60 nanometers)^3)  3e5 e-$

Indeed, the intracellular concentration would need to reach almost 25 molar for these results to be explained.

This is actually not too extreme. Bacteriophages can reach 3 M.

"Osmotic Shock and the Strength of Viral Capsids"

For an impermeable virus like the even-numbered T's, the inside salt concentration is set by the incubation solution's value of nb. Anderson et al. (1953) found in the case of T6, upon rapid dilution with distilled water, for example, that incubation nb values on the order of 1.5 M were required for osmotic shock. From Eq. 2, and n0 ≈ 3 M, it follows that nin ≈ 0.62 M and hence n++ n− ≈ 4.2 M, which because of the Donnan equilibrium is indeed significantly larger than 2nb ≈ 3 M.

https://www-sciencedirect-com.ezproxy.library.yorku.ca/science/article/pii/S0006349503744555

### 2020-11-18 documents/fluorescence.tex
e
Tube 3
data

\begin{document}

@@

Nanodrop, using 280 nm absorbance.

@@

>>>>

%!TeX root = fluroescence
\documentclass[paper.tex]{subfiles}
\begin{document}

If time-domain filtering is sufficient,

@@

Contrary to standard microscopy, you want as little excitation light to enter the objective as possible. Using the existing

Nanodrop, using 280 nm absorbance. They're also \$10,000.

@@

However, we had no luck with precipitation.

Luckily, a recent paper has the answer: direct fluorescent detection of DNA in solution, outside using dyes that bind to (intercalate into) DNA. GelGreen doesn’t penetrate.

As noted by [xi?], this is a saturating effect; if too many flurophores intercalate into the DNA the fluorescence is weaker. A “1/4000” solution of GG in distilled water mixed 50/50 with the sample (“1/8000”) worked great in our case.

(Phi6 uses an RNA - many dyes have different responses to single-stranded (ss)DNA, dsDNA, or

With the setup we’re using and the small quantities, the excitation light is somewhere around ~10^5 times as powerful as the emission. This doesn’t seem to be a big issue gel-docs, picking out bands on gels - they don’t usually seem to use excitation filters; however, to get the excitation bleed-through low enough to do this quantitative assay, the bleed-through must be really low, and in our testing proper dielectric filters are required on both the excitation and emission sides.

There are a few sources of noise:

PMT dark counts
Some be filtered out by judicious use of comparator pulse height threshold, the lock-in takes care of it. A non-issue in our case.
Ambient light leakage
Using microscope optics and the lock-in, essentially a non-issue for use, surprisingly. Some fluorescence microscopes use micron-size apertures to limit the depth of field to avoid Putting 
Figure out the average current limit for your PMT, the expected voltage based on your load resistor value and watch that it never exceeds it. It’ll be fine. Even with the room lights

Note that PMTs are happy to endure very high pulse currents, like flashbulbs for exciting.

No shutters or anything required.

The PMT was at maximum sensitivity (in fact, slightly above max voltage)

Gel-docs , with spectra specified using the Wratten scale. These do not seem to have optical density (OD - logarithmic value of transmission in the blocking band) values sufficient for this qfluor.

Epiflurorescence means the Most commercial microscopes use dichroic beamsplitters, allowing the excitation beam beam to go through the same objective. The dichroic only removes the excitation to the 1\% level - you still need the dielectric filters, and they’re really expensive. With fiber optic excitation at right angles to the objective, scattering was low enough that the dichroic was completely unnecessary.

You might be wondering why the filters are even required - why not just subtract the excitation bleed-through with a control? Unfortunately, any miniscule variation in the scattering of the excitation will be orders of magnitude larger than the fluorescence signal you’re looking for.

Some papers discuss adding a third chopper or gate period or photomultiplier or to measure the drift of the excitation light source.

Gating the photomultiplier HV is another technique.

PCR is another method

I thought the pulse height

An even better Phase-shift time domain fluorimetry. Iwata use a 20 MHz DSO to measure a 5 ns $\tau$ fluorophore. However, this involves a light source with a fast modulation bandwidth; and in the implementation they describe, the PMT must be in the voltage mode.

Called time-correlated photon counting.

Then your

Cree recommends staying below 300\% of the continuous power when modulating an LED.

While there are ways to deconvolve a slow falling edge, there’s another problem: per time interval, the time spent in the excitation-off, flurophore exponential decay time is proportional to the frequency of the excitation light. If you’re only getting 1000 photons from the sample per second, the dye lifetime is 5 ns, and you’re turning the light on and off at 1 MHz, you’re only getting a [] photons from the exponential decay region. Even with a long exposure, that doesn’t seem to be enough to pick up the decay.

Another way to pick up this phase shift is to make your lock-in amplifier phase-sensitive - very simple (a 2x clock put into a flip-flop divider, then the middle). This also wasn’t nearly good enough, completely useless.

Simple spectrally-filtered intensity is good enough.

Contrary to luminescence, you have control over when the excitation and emission light turns on, so you can do a lock-in. This doesn’t subtract the excitation bleed-through, but it

Polarization is a neat way to filter; linearly polarize the excitation, the emission comes out whatever orientation the DNA happens to be, which is usually random. Apparently

\end{document}

### 2020-11-18 documents/pamphlet.tex
Quick ol' FDTD sim of lung
data

\documentclass[fleqn,10pt]{paper}

@@

Both the microwave and microbiology components of this field appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}. Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.

>>>>

%!TeX root = pamphlet
\documentclass[fleqn,10pt]{paper}

@@

Both the microwave and microbiology components of this field appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, , \cite{Comprehensive2018}. Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.

### 2020-11-18 documents/personal_device.tex
data

This is perhaps most readily illustrated with the HB100 radar module. This device implements a complete doppler radar with two RF MOSFETS and a dielectric resonator. It operates at 10.6 GHz, yet are produced for under \$3. The PCB is stock FR4.

>>>>

This is perhaps most readily illustrated with the commercial HB100 radar module. This device implements a complete Doppler radar with two RF FETs and one dielectric resonator on a standard FR4 substrate. It operates at 10.6 GHz, yet are produced for under \$3.

### 2020-11-18 documents/sic_susceptor.tex
data

\documentclass[fleqn,10pt]{paper}

\usepackage[left=2cm,right=2cm,
top=0.5cm,
bottom=1.5cm,%
headheight=11pt,%
letterpaper]{geometry}

\include{preamble}

\title{{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation}

\begin{document}

@@

To verify that we can detect a resonance with this setup, we use the microwave susceptor mixture described by \cite{Effect2016}, which can be tuned to the correct range by varying the concentration of SiC to binder. We use the S-1 mixture.

0.6g 2000-mesh silicon carbide powder was added to 1.4 g white Elmer's glue, mixed manually until homogeneous,
applied to a mylar film, and dried with a hair dryer. A small wafer of the hardened mixture, perhaps 0.3 mm thick, 5 mm x 2 mm, was placed directly on top of the coplanar waveguide.

The spectrum was then captured, averaging (?10) sweeps of the VCO. The background spectrum was taken without the wafer in place.

@@

\cite{Effect2016} measures a peak at about 7.2 GHz. Our peak is at approximately 7.849 GHz, which is well within variation in powder grain sizes and concentration.

The paper specifies the reflection loss, S$_{11}$. Unfortunately, having no directional couplers, it is probably not possible to directly determine S$_{21}$ and S$_{11}$ with this setup.

Naively, we might expect the peak to appear as a decrease at both sensors; instead it appears as an increase in transmission and decrease in reflection. It could be possible that the presence of the dielectric wafer has merely detuned an existing resonance, that the peak is a coincidence, and that these data mean nothing.
The raw voltage plots do not suggest that this is the case; but it is nonetheless concerning.

>>>>

%!TeX root = sic_susceptor
\documentclass[paper.tex]{subfiles}
\begin{document}

@@

To verify that we can detect a resonance with this setup, we use a microwave susceptor mixture described by \cite{Effect2016}, which can be tuned to the correct range by varying the concentration of SiC to binder. We used the S-1 mixture.

0.6g 2000-mesh silicon carbide powder was added to 1.4 g white Elmer's glue, mixed manually until homogeneous,
 applied to a Mylar film, and dried with a hair dryer. A small wafer of the hardened mixture, perhaps 0.3 mm thick, 5 mm x 2 mm, was placed directly on top of the coplanar waveguide.

The spectrum was then captured, averaging multiple sweeps of the VCO. A background spectrum was taken without the wafer in place, and then the two sweeps were subtracted.

@@

\cite{Effect2016} measures a peak at about 7.2 GHz. Our peak is at approximately $7.84 \pm \approx 0.25$ GHz, which is well within variation in powder grain sizes and concentration.

The paper specifies the reflection loss, S$_{11}$. Unfortunately, having not designed in directional couplers, it is probably not possible to directly determine S$_{21}$ and S$_{11}$ with this setup.

Naively, we might expect the peak to appear as a decrease at both sensors; instead it appears as an increase in the far sensor and decrease in the near sensor. It could be possible that the presence of the dielectric wafer has merely detuned an existing resonance, that the peak is a coincidence, and that these data mean nothing.

The raw voltage plots do not suggest that this is the case; but it is nonetheless concerning.
